---
title: "Análisis del Dataset Mundial WDI del Banco Mundial"
author: "Mathew Cordero e Ian Ugalde"
output: 
  html_notebook:
    toc: true
    toc_depth: 2
    code_folding: hide
---
# 1) Grafico 1

```{r setup, include= FALSE}
# Fijar el working directory al del .Rmd
if (interactive() && requireNamespace("rstudioapi", quietly = TRUE)) {
  setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
}

knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(plotly)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*. ##Introducción Introducción \# Introducción En este análisis se presenta la historia de los datos sobre ..., se cargan las bases de datos, se limpian y se generan visualizaciones clave.



```{r}
source("Codigo/ImportDataset.R", local = knitr::knit_global())
```

```{r}
source("Codigo/ScatterPlotPIBvsEsperanzaVida4.R", local = knitr::knit_global())
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
